Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?

### 2022-10-31 Paper.Rmd
a big leap on formatting

---
title: 'Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?'
bibliography: references.bib
link-citations: yes
output:
  bookdown::pdf_document2: 
    fig.caption: yes
    includes:
      in_header: non-float-fig.tex
    toc_depth: 4
---

@@

@@

```{r Reg-Results, results='asis'}
stargazer(list("Search Tobit" = search_tobit,
               "Experience Tobit" = experience_tobit,
               "Search Linear" = search_lm,
               "Experience Linear" = experience_lm),
          type = "latex",
          header = FALSE,
          model.numbers = FALSE,
          column.labels = c("Search", "Experience", "Search", "Experience"),
          covariate.labels = c("Rating", "Rating Squared", "log10(Review Length)",
                               "log10(Total Vote)", "log10(Freshness + 1)",
                               "Positive Proportion",  
                               "Negative Proportion", "Rating x Review Length"),
          star.cutoffs = c(0.05, 0.01, 0.001),
          label = "tab:Reg-Results")
```

>>>>

---
documentclass: report
title: 'Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?'
bibliography: references.bib
csl: apa.csl
link-citations: yes
output:
  bookdown::pdf_document2:
    fig.caption: yes
    includes:
      in_header: [non-float-fig.tex, custom.tex]
    toc_depth: 4
geometry: left=40mm, right=20mm, top=30mm, bottom=30mm
fontsize: 12pt
papersize: A4
linestretch: 1.25
fontfamily: times
---

@@

\newpage

@@

```{r Reg-Results, results='asis'}

stargazer(list("Search Tobit" = search_tobit,
               "Experience Tobit" = experience_tobit,
               "Search Linear" = search_lm,
               "Experience Linear" = experience_lm),
          type = "latex",
          notes.align = "l",
          header = FALSE,
          model.numbers = FALSE,
          column.labels = c("Search", "Experience", "Search", "Experience"),
          covariate.labels = c("Rating", "Rating Squared", "log10(Review Length)",
                               "log10(Total Vote)", "log10(Freshness + 1)",
                               "Positive Proportion",  
                               "Negative Proportion", "Rating x Review Length"),
          star.cutoffs = c(0.05, 0.01, 0.001),
          label = "tab:Reg-Results")
```

\newpage
